---
title: "Hw1"
output: html_document
---

# Question 1

Variables

```{r}
tv=c(44, 47, 50, 71, 33, 42, 46, 52, 39, 55, 62, 70, 44, 49, 50)
happiness=c(256, 251, 267, 376, 170, 210, 322, 274, 215, 272, 337, 368, 224, 276, 294)
```

analysis

```{r}
model = lm(happiness~tv)
summary(model)
```

## a) Estimate the regression line:

Y = 21.062 + 5.035(tv)

## b) Interpret B_o and B_1:

B_o is the baseline happiness where everyone, regardless of how much tv they watch

B_1 is the unit of increase in happiness per unit value increase of tv watched

## c) Test whether or not a linear association exists between happiness and amount of tv one watches. State your hypotheses and your conclusions.

Ho = B1 = 0

```{r}
5.035/0.605
```

p value of 1.45e-06 \> 0.05 means we can not reject the null, therefore there is not a linear association between hapiness and amount of tv one watches.

## d) Interpret R\^2

R\^2 represents the proportion of variance in the dependent variable that is predictable from the independent variable.

since R\^2=0.8429, about 84% of the variance of happiness is explained by the predictor variable of amount of tv watched.

## e) plot the estimated regression line and the data.

```{r}
plot(tv, happiness, abline(lm(happiness~tv)))
```

## f) Verify the assumptions

```{r}
par(mfrow = c(2,2))
plot(model)
```

Linearity: Plot 1 shows no curve; relatively flat therefore confirming linearity

Constant Variance: Plot 1 shows no funnel shape confirms constant variance

Normality: Plot 2 shows values that align relatively well around a trendline; therefore normality is confirmed.

Outlier: value 7 deviates from other values in the plots revealing that it is an outlier

## Notes

plot 1 tests assumptions of linearity and constant variance.

-   a curve here would indicate assumption of linearity is violated.

-   a funnel indicates constant variance is violated.

-   random scatter around zero means we pass both assumptions of linearity and constant variance

Plot 2: Normal Q-Q plot

-   tests normality:

    -   normal: linear line

    -   violation: no line
